---
title: "Writing Functions"
output: github_document
---

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Z-scores!!

Let's compute the z-score version of a list of numbers.

```{r}
x_vec = rnorm(25, mean = 7, sd = 4)

(x_vec - mean(x_vec)) / sd(x_vec)
```

Suppose you want to do this often.

**NAME OF FUNCTION** = function(**ARGUEMENTS**) {
  
  **BODY OF FUNCTION**
}

```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)) {
    stop("Z scores only work for numbers")
  }
  
  if (length(x) < 3) {
    stop("Z scores really only work if you have three or more numbers")
  }
  
  z = (x - mean(x)) / sd(x)
  
  z
  
}
```


```{r}
z_scores(x = x_vec)

z_scores(x = 1:10)
z_scores(x = rbinom(1000, 1, .6))

# z_scores(x = 2) # not working
# z_scores(x = "my name is jeff") # not working either
```


## Let's have multiple outputs

Let's just get the mean and sd from the vector input.

```{r}
mean_and_sd = function(x) {

  if (!is.numeric(x)) {
    stop("Z scores only work for numbers")
  }
  
  if (length(x) < 3) {
    stop("Z scores really only work if you have three or more numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
  
}

mean_and_sd(x = x_vec)
mean_and_sd(x = 1:10)
mean_and_sd(x = rbinom(1000, 1, .5))

# mean_and_sd(x = 1)
```


## Let's start with simulations ...

```{r}
x_vec = rnorm(n = 25000, mean = 17, sd = 4)

tibble(
  mean = mean(x_vec),
  sd = sd(x_vec)
)
```

Can I do this using a function ...

```{r}
sim_mean_sd = function(n_obs, true_mean = 7, true_sd = 4) {
  
  x = rnorm(n = n_obs, mean =  true_mean, sd = true_sd)
  
  
  tibble(
    mean = mean(x),
    sd = sd(x)
  )
  
}

sim_mean_sd = function(n_obs, true_mean = 7, true_sd = 4) {
  
  x_inside_of_function = rnorm(n = n_obs, mean =  true_mean, sd = true_sd)
  
  
  tibble(
    mean = mean(x_inside_of_function),
    sd = sd(x_inside_of_function)
  )
  
}

# x_inside_of_function (does not exist)
```

does it work?

```{r}
sim_mean_sd(n_obs = 25, true_mean = 100, true_sd = 1)
sim_mean_sd(n_obs = 2500)
sim_mean_sd(2500)
```


## Fixing bad stuff


```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```


Let’s write a function to get reviews.

```{r}
read_page_reviews = function(url){
  
  dynamite_html = read_html(url)
  
  review_titles = 
    dynamite_html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()

  review_stars = 
    dynamite_html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    dynamite_html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim() %>% 
    str_subset("The media could not be loaded.", negate = TRUE) %>% 
    str_subset("^$", negate = TRUE)
  
  reviews = tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
  
  reviews
  
}

read_page_reviews(url)
```


```{r}
base_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

vec_urls = str_c(base_url, c(1, 2, 4, 5))

vec_urls = str_c(base_url, 1:5)

dynamite_reviews =
  bind_rows(
    read_page_reviews(vec_urls[1]),
    read_page_reviews(vec_urls[2]),
    read_page_reviews(vec_urls[3]),
    read_page_reviews(vec_urls[4]),
    read_page_reviews(vec_urls[5])
  )
```


```{r}
fellowship_ring = readxl::read_excel("./data/LotR_Words.xlsx", range = "B3:D6") %>%
  mutate(movie = "fellowship_ring")

two_towers = readxl::read_excel("./data/LotR_Words.xlsx", range = "F3:H6") %>%
  mutate(movie = "two_towers")

return_king = readxl::read_excel("./data/LotR_Words.xlsx", range = "J3:L6") %>%
  mutate(movie = "return_king")

lotr_tidy = bind_rows(fellowship_ring, two_towers, return_king) %>%
  janitor::clean_names() %>%
  gather(key = sex, value = words, female:male) %>%
  mutate(race = str_to_lower(race)) %>% 
  select(movie, everything())
```

Write a function to achieve it?

```{r}
lotr_load_and_tidy = function(path, range, movie_name) {
  
  df = readxl::read_excel(path, range = range) %>%
    janitor::clean_names() %>%
    gather(key = sex, value = words, female:male) %>%
    mutate(race = str_to_lower(race),
           movie = movie_name)
  
  df
  
}

lotr_tidy = 
  bind_rows(
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "B3:D6", "fellowship_ring"),
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "F3:H6", "two_towers"),
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "J3:L6", "return_king")) %>%
  select(movie, everything()) 
```

